Solving the Poisson-equation in one dimension: \\ \normalsize{TDMA vs LU} \\ \hrulefill\small{ FYS3150: Computational Physics }\hrulefill

### 2018-10-13 Project1/article/article.tex
Typo
Removed numbering of dots (not really equations)

\begin{equation}
\left[
\begin{array}{cccc|c}
b_1 & c_1 & 0 & 0 & f_1 \\
a_2 & b_2 & c_2 & 0  & f_2 \\
0 & a_3 & b_3 & c_3 & f_3 \\
0 & 0 & a_4 & b_4 & f_4
\end{array}
\right] \sim
\left[
\begin{array}{cccc|c}
1 & c_1/b_1 & 0 & 0 & b_1/b_1 \\
0 & b_2-\frac{c_1}{b_1}a_2 & c_2 & 0  & f_2-\frac{f_1}{b_1}a_2 \\
0 & a_3 & b_3 & c_3 & f_3 \\
0 & 0 & a_4 & b_4 & f_4
\end{array}
\right]
\end{equation}
Now let $\beta_1=b_1$ and $\beta_2=b_2-\frac{c_1}{b_1}a_2$. As new
elements start to appear in vector $\vb{f}$, right to the vertical bar
in the augmented matrix, they are also relabeled to $\tilde{f}_i$. For
example $\tilde{f}_1=f_1/\beta_1$. One more iteration will reveal the
pattern of the algorithm.

@@

The equation $A\vb{v}=LU\vb{v}=\vb{f}$ can be solved in two steps
\begin{equation}
L\vb{w}=\vb{f}, \quad U\vb{v}=\vb{w}
\end{equation}
Written out, the full set of these linear equations will look like
\begin{align}
w_1 &= f_1 \label{eq:LU1}\\
l_{21}w_1 + w_2 &= f_2 \\
l_{31}w_1 + l_{32}w_2 +w_3 &= f_3 \\
 & \vdots \\
l_{n-11}w_1 + l_{n-12}w_2 + l_{n-13}w_3 + \dots + w_{n-1}  &=
                                                                    f_{n-1}\\
l_{n1}w_1 + l_{n2}w_2 + l_{n3}w_3 + \dots + l_{nn-1}w_{n-1} + w_n &=
                                                                    f_n
  \label{eq:LU2}\\  
u_{11}v_1 + u_{12}v_2 + u_{13}v_3 + \dots + u_{1n-1}v_{n-1} +
  u_{1n}v_n &= w_1  \label{eq:LU4}\\  
u_{22}v_2 + u_{23}v_3 + \dots + u_{2n-1}v_{n-1} + u_{2n}v_n &= w_2 \\
u_{33}v_3 + \dots+u_{3n-1}v_{n-1} + u_{3n}v_n &= w_3 \\
 & \vdots \\
u_{n-1n-1}v_{n-1} &=  w_{n-1} \\
u_{nn}v_n &= w_n \label{eq:LU3}
\end{align}
First $\vb{w}$ can be determined by iterating forwards through
equations \ref{eq:LU1} to \ref{eq:LU2}. Then $\vb{v}$ can be found be
iterating backwards from equation \ref{eq:LU3} to equation
\ref{eq:LU4}.

>>>>

\begin{equation}
\left[
\begin{array}{cccc|c}
b_1 & c_1 & 0 & 0 & f_1 \\
a_2 & b_2 & c_2 & 0  & f_2 \\
0 & a_3 & b_3 & c_3 & f_3 \\
0 & 0 & a_4 & b_4 & f_4
\end{array}
\right] \sim
\left[
\begin{array}{cccc|c}
1 & c_1/b_1 & 0 & 0 & f_1/b_1 \\
0 & b_2-\frac{c_1}{b_1}a_2 & c_2 & 0  & f_2-\frac{f_1}{b_1}a_2 \\
0 & a_3 & b_3 & c_3 & f_3 \\
0 & 0 & a_4 & b_4 & f_4
\end{array}
\right]
\end{equation}
Now let $\beta_1=b_1$ and $\beta_2=b_2-\frac{c_1}{b_1}a_2$. As new
elements start to appear in vector $\vb{f}$, right to the vertical bar
in the augmented matrix, they are also relabeled to $\tilde{f}_i$. For
example $\tilde{f}_1=f_1/\beta_1$. One more iteration will reveal the
pattern of the algorithm.

@@

The equation $A\vb{v}=LU\vb{v}=\vb{f}$ can be solved in two steps
\begin{equation}
L\vb{w}=\vb{f}, \quad U\vb{v}=\vb{w}
\end{equation}
Written out, the full set of these linear equations will look like
\begin{align}
w_1 &= f_1 \label{eq:LU1}\\
l_{21}w_1 + w_2 &= f_2 \\
l_{31}w_1 + l_{32}w_2 +w_3 &= f_3 \\
 & \vdots \nonumber \\
l_{n-11}w_1 + l_{n-12}w_2 + l_{n-13}w_3 + \dots + w_{n-1}  &=
                                                                    f_{n-1}\\
l_{n1}w_1 + l_{n2}w_2 + l_{n3}w_3 + \dots + l_{nn-1}w_{n-1} + w_n &=
                                                                    f_n
  \label{eq:LU2}\\  
u_{11}v_1 + u_{12}v_2 + u_{13}v_3 + \dots + u_{1n-1}v_{n-1} +
  u_{1n}v_n &= w_1  \label{eq:LU4}\\  
u_{22}v_2 + u_{23}v_3 + \dots + u_{2n-1}v_{n-1} + u_{2n}v_n &= w_2 \\
u_{33}v_3 + \dots+u_{3n-1}v_{n-1} + u_{3n}v_n &= w_3 \\
 & \vdots \nonumber \\
u_{n-1n-1}v_{n-1} &=  w_{n-1} \\
u_{nn}v_n &= w_n \label{eq:LU3}
\end{align}
First $\vb{w}$ can be determined by iterating forwards through
equations \ref{eq:LU1} to \ref{eq:LU2}. Then $\vb{v}$ can be found be
iterating backwards from equation \ref{eq:LU3} to equation
\ref{eq:LU4}.
